### 2023-02-22 main.tex
Fixed
ll
refs
Update main.tex

G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=(2x+N)^{N-1}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-(N-1)}B_{2}(x)\ldots B_{N}(x)

@@

\begin{equation}\label{SecondProperty}

@@

@@

@@

>>>>

G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&(2x+N)^{2-N+k_{2}+\ldots+k_{N}}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{N-2-k_{2}+\ldots-k_{N}}\\&B_{2}^{k_{2}}(x)\ldots B_{N}^{k_{N}}(x)
Let us notice that when all $k$'s are one, we have again the expression (2.17) of the 2 species case \cite{frassek2020eigenstates}. 

@@

\item Property one: (this is the equivalent of equation (2.19) of \cite{frassek2020eigenstates})\begin{equation}\label{SecondProperty}

@@

Indeed take for example $i=2$
G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)&=(2x+N)(2x+N)^{2-N+k_{2}-1+k_{3}\ldots+k_{N}}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}
\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{N-2-k_{2}+1-k_{3}-\ldots-k_{N}} B_{2}(x)B_{2}(x)^{k_{2}-1}B_{3}^{k_{3}}(x)\ldots B_{N}^{k_{N}}(x) 
\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N}}^{k_{2}-1,k_{3},\ldots,k_{N}}(x)
\item Property two: (this is the equivalent of equation (2.20) of \cite{frassek2020eigenstates})

@@

{\color{blue}This second property can be proved by using a lower weight representation }

@@

	\\&+\ldots +
